%\section{Introduction}
\section{Motivation} 
Glaucoma is one of the most painful diseases caused by excessive levels of pressure in the eyes which creates a permanent loss of vision. It is also known as the ‘silent thief of sight’ as it cannot be detected at an early stage [1]. We are going to use Explainable AI (XAI) to classify scanned images of eyes that have glaucoma. XAI proposes the report to the decision of Artificial Intelligence which means Deep Learning or Black Box to the extent that is human interpretable. Deep Learning (DL) is a subset of Artificial Intelligence (AI) dependent on profound neural networks which have made striking leaps forwards in clinical imaging, especially for image characterization and pattern acknowledgment [2]. The use of Deep Learning (DL) is increasing in glaucoma research because these models can accomplish high precision, issues with trust, interpretability, and experimental utility structure hindrances to occurring clinical practice. The main purpose of this study is to represent whether and how deep learning-based measurements can be utilized for glaucoma execution in the clinic [3].

\vspace{5mm}
In our glaucoma dataset, we have some features for suspicious glaucoma and non-suspicious glaucoma. However, data visualization methods aim to produce more transparent and explainable decisions. In addition, CNN Based models are visually explainable for decision making and have gained significant attention in image classification [4]. A few works focus on preparing a Convolution Neural Network (CNN) by brute force while others use division and element extraction methods to identify glaucoma [5]. To apply for XAI we took Conventional Neural Network (CNN), Support Vector Machine (SVM), and Fully Connected Neural Network (FCNN). XAI frameworks such as LIME, SHAP, ELI5, AIX360, Skater are used for building trust among humans about the decisions made by AI models which are possibly making the black box models more transparent. Moreover, working with these AI models is not understandable by the common man and professionals. Additionally, AI and Machine Learning are essential for building trust among humans for decision making which is only possible by making black-box models more transparent through Explainable AI Frameworks which tries to explain their working.

\section{Introduction}
Glaucoma is a gathering of eye illnesses wherein the optic nerve is harmed prompting irreversible loss of vision. By and large, this is because of an expanded pressing factor inside the eye. The eye creates a liquid called fluid humor which is emitted by the ciliary body into the back chamber - a space between the iris and the focal point. It at that point courses through the apprentice into the foremost chamber between the iris and the cornea. From here, it channels through a wipe-like design situated at the foundation of the iris considered the trabecular meshwork, and leaves the eye. In a solid eye, the pace of discharge adjusts the pace of seepage. In individuals with glaucoma, the seepage waterway is part of the way or totally hindered. Liquid develops in the chambers and this expands pressure inside the eye. The pressing factor drives the focal point back and pushes on the glassy body which thus packs and harms the veins and nerve strands running at the rear of the eye. These harms bring about patches of vision misfortune, and whenever left untreated, may prompt absolute visual impairment. There are two significant kinds of glaucoma: open-angle and angle-closure.

\vspace{5mm}
Open-angle glaucoma, or chronic glaucoma, is brought about by an incomplete blockage of the waste trench. The point between the cornea and the iris is "open", which means the passageway to the waterway is clear, however, the progression of watery humor is more slow than typical. The pressing factor develops continuously in the eye throughout a significant period. Side effects show up continuously, beginning from fringe vision misfortune, and may go on unseen until focal vision is influenced. Movement of glaucoma can be halted with medicines, however, part of the vision that is now lost can't be reestablished. This is the reason it's vital to distinguish early indications of glaucoma with standard eye tests.

\vspace{5mm}
Angle-closure glaucoma, or acute glaucoma, is brought about by an abrupt and complete blockage of fluid humor waste. The pressing factor inside the eye rises quickly and may prompt absolute visual deficiency rapidly. Certain anatomical highlights of the eye, for example, limited seepage point, shallow foremost chamber, slender and saggy iris, make it simpler to foster intense glaucoma. Commonly, this happens when the understudy is expanded and the focal point has adhered to the rear of the iris. This squares the fluid humor from coursing through the understudy into the foremost chamber. Collection of liquid in the back chamber pushes on the iris, making it swell outward and square the waste point. Acute angle-closure glaucoma is a visual crisis and requires quick consideration.

\vspace{5mm}
However, it's one of the leading causes of blindness for people over the age of 60. Statistics show that even with the treatment 15\% to 20\% of patients become blind. For this reason, in this research, we are going to apply Explainable AI to detect Glaucoma in a better way than exists. As the diagnosis of glaucoma is a complicated and expensive process, the application of a Deep Neural network leveraging XAI can give more improvement in understanding or detecting many problems related to glaucoma disease.

\section{Research Objectives}
The field of Explainable Artificial Intelligence has filled dramatically lately with innovations, techniques, and applications arising at a fast rate. A considerable lot of these progressions have been utilized to improve the conclusion and the executives of glaucoma. We intend to give an outline of ongoing distributions in regards to the utilization of man-made consciousness to improve the recognition and treatment of glaucoma.

\vspace{5mm}
According to modern medical science, glaucoma is diagnosed in four different ways. Initially, glaucoma is diagnosed by machine where the pressure is measured inside the eye. Here the whole diagnostic test is called Tonometry and the intraocular pressure is measured throughout this process. Apart from this, there is a prerequisite of this test which is a visual feel test. In this test, the patient is asked to close one eye and the doctor moves his hand from top to bottom, bottom to top, left to right, and right to left. In this way, the doctor checks the patient’s visibility through one eye. Moreover, there is another way of diagnosing glaucoma which is the Imaging Test where the main motive is to check the depth of eyes by showing pictures. However, the final diagnosis is pachymetry where pachymetry is a medical device that is used to measure the thickness of the eye’s cornea. In the above ways, glaucoma can be diagnosed and partial or complete blindness could be prevented.

\vspace{5mm}
AI classifiers and deep learning algorithms have been created to self-sufficiently recognize early primary and useful changes of glaucoma utilizing diverse imaging and testing modalities like fundus photography, optical cognizance tomography, and standard computerized perimetry. Artificial Intelligence has additionally been utilized to further portray structure-work connection in glaucoma. Additionally, “structure-structure” predictions have been effectively assessed. Other AI strategies using complex measurable demonstrating have been utilized to distinguish glaucoma movement, just as to foresee future movement. Though not yet endorsed for clinical use, these artificial intelligence methods can essentially improve glaucoma analysis and the board.

\nomenclature{$XAI$}{Explainable AI}
\nomenclature{$DL$}{Deep Learning}
\nomenclature{$AI$}{Artificial Intelligence}
\nomenclature{$CNN$}{Convolution Neural Network}
\nomenclature{$SVM$}{Support Vector Machine}
\nomenclature{$FCNN$}{Fully Connected Neural Network}
\nomenclature{$LIME$}{Local Interpretable Model-agnostic Explanations}
\nomenclature{$SHAP$}{SHapley Additive exPlanations}