%\section{Background}
\section{Problem Statement} 
Glaucoma is a very common group of eye diseases caused by damage to the optic nerve that connects the eye to the brain and if untreated, it causes permanent loss of vision. It is the second most popular cause of blindness globally. As per experiments, it is tracked down that the conclusion of the experts or ophthalmologists is abstract. This may cause a few misinterpretations when the glaucoma is distinguished as inaccurate, for example, false-positive and false-negative cases. Likewise, glaucoma is asymptomatic in the beginning phase. The harm advances gradually and it has no manifestations or early admonition signs until the vision is lost in the later stage. Additionally, if it tends to be distinguished in the beginning, the visual sight will be saved. It is shown that treatment and standard tests can forestall vision misfortune in individuals just at a beginning phase. On the other hand, if the vision loss has already occurred, the treatment can delay or hinder further vision loss [6].

\vspace{5mm}
\noindent There are mainly two types of glaucoma. Primary glaucoma also called chronic glaucoma is caused by prolonged intraocular pressure in the eye whereas secondary glaucoma is caused by sudden events such as an injury to the eye or inflammation in the eye or the use of steroids. Both primary and secondary glaucoma can be further classified as open-angle glaucoma and closed-angle glaucoma. Open-angle glaucoma is the most common form of glaucoma and is responsible for 90\% of the cases [7].  In open-angle glaucoma, there is a wide and open angle between the cornea and iris. But in the case of closed-angle glaucoma, the angle is much narrower. Each of these subdivisions can be further divided into classes depending on conditions such as acute, intermittent, chronic, post status, etc. And there are other minor variants of glaucoma such as pigmentary glaucoma, exfoliation glaucoma, primary juvenile glaucoma, etc. In traditional cases, Ophthalmologists use Optical Coherence Tomography or OCT for detecting Glaucoma. Optical Coherence Tomography or OCT is generally utilized for clinical imaging methods. OCT is an optical sign procurement and preparation strategy that catches optic pictures in a three-dimensional picture. Both OCT and ophthalmologists are having a similar issue which is lacking and costly. They must be found in enormous emergency clinics or private emergency clinics. Some glaucoma patients are deficient assets. This can make patients seek a late glaucoma treatment and be awful for their eye wellbeing. The requirement for specialists and a lot of costs are constraints of potential in mass evaluating for early discovery. To take care of the issue of OCT pictures, fundus im-ages are chosen to be input pictures for this venture. A fundus camera is one more sort of camera that can be utilized to catch retina pictures. Fun-does camera has more affordable costs contrasting and OCT pictures. It very well may be found in each region's clinical focus, not just enormous clinics like OCT. Fundus pictures can be utilized for glaucoma finding through the CDR strategy [8].

\vspace{5mm}
\noindent Since glaucoma is such a prominent reason for blindness around the world, we must apply our knowledge of classification techniques to classify the various types of glaucoma for the betterment of the world. However, we are portraying and evaluating Convolutional Neural Organization (CNN) models for the discovery of glaucoma dependent on Optical Coherence Tomography (OCT) Retinal Nerve Fiber Layer (RNFL) likelihood maps. Such CNN models can work in pairs with human specialists to keep up with large eye health and assist recognition of visual deficiency causing eye sickness []. We can easily use binary classifiers to differentiate between images of primary glaucoma and secondary glaucoma and then we can use another binary classifier to differentiate between images of open-angle glaucoma and closed-angle glaucoma. In this study, we are going to use Explainable AI (XAI) to classify scanned images of eyes that have glaucoma.

\nomenclature{$OCT$}{Optical Coherence Tomography}